Simulation pipeline

### 2021-07-08 Analysis/02_Simulation_pipeline.Rmd
results up

```{r, eval = FALSE}
source("../Functions/analyse.replicates.R")
## Check the change in variance for all 120 parameters
analyse.replicates("../Data/Processed/sim_filtering.rda") #140
analyse.replicates("../Data/Processed/sim_equalizing.rda") #155
analyse.replicates("../Data/Processed/sim_facilitation.rda") #126
analyse.replicates("../Data/Processed/sim_competition.rda")
```

>>>>

```{r, eval = FALSE}
source("../Functions/analyse.replicates.R")
## Check the change in variance for all 120 parameters
analyse.replicates("../Data/Processed/sim_filtering.rda") #140
analyse.replicates("../Data/Processed/sim_equalizing.rda") #155
analyse.replicates("../Data/Processed/sim_facilitation.rda") #126
analyse.replicates("../Data/Processed/sim_competition.rda") #163
```
